P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2024-07-04 sage_latex_template/manuscript.tex
Fix code syntax hl
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

\lstset{
    showstringspaces=false,
    extendedchars=true,
    basicstyle=\footnotesize\ttfamily,
    commentstyle=\slshape,
    stringstyle=\ttfamily,
    breaklines=true,
    breakatwhitespace=true,
    columns=flexible,
    numbers=left,
    numberstyle=\tiny,
    basewidth=.5em,
    xleftmargin=.5cm,
    captionpos=b,
    frame=lines
}

@@

\begin{lstlisting}[language=Python,
                   label={lst:build_neigh},
                   caption={Neighbor-lists intermediate representation construction in P4IRS.}]
class BuildNeighborLists(Lowerable):
  # ...
  @pairs_device_block
  def lower(self):
    # ...
    sim.module_name("build_neighbor_lists")
    sim.check_resize(sim.neighbor_capacity, neighbor_lists.numneighs)

    for i in ParticleFor(sim):
      for shape in range(sim.max_shapes()):
        Assign(sim, neighbor_lists.numneighs[i][shape], 0)

@@

      neighs_start = sum([neighbor_lists.numneighs[i][s] for s in range(shape)], 0)
      numneighs = neighbor_lists.numneighs[i][shape]
      Assign(sim, neighbor_lists.neighborlists[i][neighs_start + numneighs], j)
      Assign(sim, neighbor_lists.numneighs[i][shape], numneighs + 1)
\end{lstlisting}

>>>>

% Custom colors
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepred}{rgb}{0.6,0,0}
\definecolor{deepgreen}{rgb}{0,0.5,0}

\lstset{
    showstringspaces=false,
    extendedchars=true,
    morekeywords={self},
    emph={ParticleFor,ParticleInteraction,Lowerable,Assign},
    basicstyle=\footnotesize\ttfamily,
    commentstyle=\slshape\color{deepgreen},
    stringstyle=\ttfamily\color{deepred},
    keywordstyle=\ttfamily\color{deepblue},
    emphstyle=\ttfamily\color{violet},
    breaklines=true,
    breakatwhitespace=true,
    columns=flexible,
    numbers=left,
    numberstyle=\tiny,
    basewidth=.5em,
    xleftmargin=.5cm,
    captionpos=b,
    frame=lines
}

@@

\begin{lstlisting}[language=Python,
                   label={lst:build_neigh},
                   caption={Neighbor-lists intermediate representation construction in P4IRS. Elements that are explicitly built for the AST (both high and low level) are shown in purple, and implicit elements such as expressions are constructed via operator-overloading and bound to a statement at some point in the construction.}]
class BuildNeighborLists(Lowerable):
  # ...
  @pairs_device_block
  def lower(self):
    # ...
    sim.module_name("build_neighbor_lists")
    sim.check_resize(sim.neighbor_capacity, numneighs)

    for i in ParticleFor(sim):
      for shape in range(sim.max_shapes()):
        Assign(sim, numneighs[i][shape], 0)

@@

      nb_start = sum([numneighs[i][s] for s in range(shape)], 0)
      n = numneighs[i][shape]
      Assign(sim, neighbors[i][nb_start + n], j)
      Assign(sim, numneighs[i][shape], n + 1)
\end{lstlisting}
